HPC On-boarding

### 2016-01-20 hpc_101/paper.tex
change table line

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
\toprule                                                                    
\toprule                                                                    
%\midrule
%\midrule
community.q & \begin{tabular}{l r} \textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} & \padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min}& \padfrom{\ \ \ }{1}~\\ \textbf{Max}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
kill.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{12}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
htc.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
lm.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ }{262100}\end{tabular}\\
\hline
sb.q & \begin{tabular}{l r}\textbf{Default} & 0-00:05:00~\\ \textbf{Max} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}

>>>>

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
%\toprule                                                                    
%\toprule                                                                    
\midrule
\midrule
community.q & \begin{tabular}{l r} \textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} & \padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min}& \padfrom{\ \ \ }{1}~\\ \textbf{Max}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
kill.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{12}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
htc.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
lm.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ }{262100}\end{tabular}\\
\hline
sb.q & \begin{tabular}{l r}\textbf{Default} & 0-00:05:00~\\ \textbf{Max} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}
